Characterization of gaps in directly bonded Si compound optics

### 2014-04-21 AO_bondedSi.tex
add another figure for large gap theory, some concommittant tweaks

\section{Si$-$air$-$Si Fabry P\`{e}rot measurement theory}
\label{secTheory}

@@

\subsection{The Si-Si interface gap is a low Finesse Fabry-P\`{e}rot etalon}

Our measurement technique exploits the large Fresnel reflection \cite{2001opt4.book.....H} at the Si-Air interface.  The refractive index of silicon at room temperature ranges from 3.55$-$3.45 from $\lambda = $ 1150$-$2500 nm \cite{2006SPIE.6273E..77F}, one of the largest refractive indices of any conventional material.  The Fresnel reflection is accordingly about 30\% per surface.  For comparison, conventional optical materials with refractive indices in the range 1.5$-$1.7 have Fresnel reflection of merely 4$-$7\% per surface.  Figure \ref{figSiIndexFinesse} shows the refractive index as a function of wavelength for room temperature, which we computed using the coefficients from \cite{2006SPIE.6273E..77F}.

@@

The Si-Si interface gap is a low-Finesse Fabry-P\`{e}rot etalon\cite{2007fuph.book.....S}.  The transmission through a Fabry-P\`{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We assume transmission is at normal incidence, the refractive index of the gap is 1.0, and the material is at room temperature.  Si is negligibly absorbing longward of $\lambda$ = 1150 nm, which we verified with comparison of Si reference samples of different thicknesses.  We compute the reflectivity for an Si$-$air interface, which is a modest function of wavelength through the refractive index of Silicon, $n(\lambda, T)$ \cite{2006SPIE.6273E..77F}, as shown in Figure \ref{figSiIndexFinesse}.  In the equations ahead we drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ for clarity.  The computation is simply Fresnel's law at normal incidence:

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.45\columnwidth]{figs/20140421_absolute.pdf}}
\caption{Modeled absolute transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figAbsoluteTrans}.  The absolute transmission through Si depends on the Si refractive index, which depends on wavelength. }
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.45\columnwidth]{figs/20140421_absoluteB.pdf}}
\caption{Modeled etalon transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figEtalonRelTrans}.  The curves are examples from a family defined in Equation \ref{eqFP}.   The limit of no gap is 100\% transmissive, compared to a DSP reference.  A 35 nm gap degrades the transmission over a DSP reference by 4\% at 1200 nm.}
\end{figure}

@@

It is clear that in the limit $\lim_{d \rightarrow 0}$, the etalon approaches 100\% transmission.  Figure \ref{figEtalonRelTrans} shows a plot of Equation \ref{eqFP} for gap sizes, $d$, of 20 nm and 35 nm.  In the next section we compare measurements to by-eye fits of this equation.

>>>>

\section{Si$-$Si Fabry P\`{e}rot measurement theory}
\label{secTheory}

@@

\subsection{The Si$-$Si interface gap is a low Finesse Fabry-P\`{e}rot etalon}

Our measurement technique exploits the large Fresnel reflection \cite{2001opt4.book.....H} at the Si$-$vacuum interface.  The refractive index of silicon at room temperature ranges from 3.55$-$3.45 from $\lambda = $ 1150$-$2500 nm \cite{2006SPIE.6273E..77F}, one of the largest refractive indices of any conventional material.  The Fresnel reflection is accordingly about 30\% per surface.  For comparison, conventional optical materials with refractive indices in the range 1.5$-$1.7 have Fresnel reflection of merely 4$-$7\% per surface.  Figure \ref{figSiIndexFinesse} shows the refractive index as a function of wavelength for room temperature, which we computed using the coefficients from \cite{2006SPIE.6273E..77F}.

@@

The Si$-$Si interface gap is a low-Finesse Fabry-P\`{e}rot etalon\cite{2007fuph.book.....S}.  The transmission through a Fabry-P\`{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We assume transmission is at normal incidence, the refractive index of the gap is 1.0, and the material is at room temperature.  Si is negligibly absorbing longward of $\lambda$ = 1150 nm, which we verified with comparison of Si reference samples of different thicknesses.  We compute the reflectivity for an Si$-$vacuum interface, which is a modest function of wavelength through the refractive index of Silicon, $n(\lambda, T)$ \cite{2006SPIE.6273E..77F}, as shown in Figure \ref{figSiIndexFinesse}.  In the equations ahead we drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ for clarity.  The computation is simply Fresnel's law at normal incidence:

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absolute.pdf}}
\caption{Modeled absolute transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figAbsoluteTrans}.  The absolute transmission through Si depends on the Si refractive index, which depends on wavelength. }
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absoluteB.pdf}}
\caption{Modeled etalon transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figEtalonRelTrans}.  The curves are examples from a family defined in Equation \ref{eqFP}.   The limit of no gap is 100\% transmissive, compared to a DSP reference.  A 35 nm gap degrades the transmission over a DSP reference by 4\% at 1200 nm.}
\end{figure}

@@

It is clear that in the limit $\lim_{d \rightarrow 0}$, the etalon approaches 100\% transmission.  Figure \ref{figEtalonRelTrans} shows a plot of Equation \ref{eqFP} for gap sizes, $d$, of 20 nm and 35 nm.  In Section \ref{secResults} we compare wavelength dependent transmission measurements to by-eye fits of Equation \ref{eqFP}.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.65\columnwidth]{figs/20140421_absoluteC.pdf}}
\caption{Modeled etalon transmission through a silicon substrate with gaps of axial extent 35 nm (red dotted curve), 350 nm (green dash-dot curve), and 3500 nm (blue long-dashed curve)\label{figEtalonRelTrans}.  The curves are examples from a family defined in Equation \ref{eqFP}.  The 3500 nm gap curve has obvious Fabry-P\`erot fringes, whereas the 35 and 350 nm gap curves vary smoothly with wavelength.  }
\end{figure}
